\green{A follow-up on intermediate-mass black hole candidates in the second LIGO--Virgo observing run with the Bayes Coherence Ratio}

### 2022-07-20 titlepage_mnras.tex
ref response 2

% % Title of the paper, and the short title which is used in the headers.
% % Keep the title short and informative.
% \title[MNRAS \LaTeX\ guide for authors]{\textit{Monthly Notices of the Royal Astronomical
%   Society}:  \LaTeX\ guide for authors}
\title[An IMBH search in O2 using the BCR]{A search for intermediate-mass black holes mergers in the \\second LIGO--Virgo observing run with the Bayes Coherence Ratio}

>>>>

% % Title of the paper, and the short title which is used in the headers.
% % Keep the title short and informative.
% \title[MNRAS \LaTeX\ guide for authors]{\textit{Monthly Notices of the Royal Astronomical
%   Society}:  \LaTeX\ guide for authors}
\title[\green{An IMBH candidate follow-up in O2 using the BCR}]{\green{A follow-up on intermediate-mass black hole candidates in the second LIGO--Virgo observing run with the Bayes Coherence Ratio}}
